Source Summaries

### 2020-02-09 paper/sourceSummaries/summary2.tex
Fixed Connor title
Initial Push for Joshua\'s source summary 2

\noindent
\subsection{Wiegand Protocol Access: A Decade of Decryption}

@@

\noindent
\subsection{Wiegand Protocol Access: A Decade of Decryption}

@@

>>>>

\noindent
\subsection{{A}nalyzing the {S}ecurity of {B}luetooth {L}ow {E}nergy}

@@

\noindent
\subsection{{W}iegand {P}rotocol {A}ccess: {A} {D}ecade of {D}ecryption}

@@

\noindent
\subsection{{S}urvey on {V}arious {D}oor {L}ock {A}ccess {C}ontrol {M}echanisms}

\noindent
Joshua Niemann

\Urlmuskip=0mu plus 1mu\relax
\bibentry{matthewrs2017surveydoorlock}

\noindent
The authors compare different types of door lock authentication measures and their overall security.

\noindent
The authors are applying Game Theory by directly comparing each individual authentication method.

\noindent
The authors directly compare different authentication methods using different factors.  These can include battery life, cryptographic and mechanical security, the concern of a passed credential, and what happens if an authentication token is lost.

\noindent
The authors found that each system has individual strengths.  As each method does better in different ways, emphasis is placed on ensuring the use of the lock that is best suited for the use case in which it is placed.  Factors considered include but are not limited to whether a physical key is required, whether or not the key will be passed off to a third party user, and if the system would be considered secure for the given use case.

\noindent
The authors suggest using the knowlege of authentication system problems in order to build a new system, taking in mind the strengths and weaknesses for each category of authentication.
